---
title: "Ikea Sales Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
Purpose of this task is to:

Demonstrate data wrangling and visualisation skills

Demonstrate knowledge and skills in developing models with a focus on classification and regression algorithms

Evaluate developed models and identify bottlenecks and improvements

Develop a solution to the business problem and communicate findings to stakeholders

Learning outcomes:

Critically analyse the role of business analytics in supporting decision making in a modern organisation, with a focus of working with different data formats and data wrangling techniques

Investigate and assess different analytics solutions in open source environments to develop effective visualisations

Evaluate analytics models to uncover hidden patterns in business data and understand relationships between variables

Deconstruct and exemplify data communication strategies through reproducible reporting and collaborative practices with version control

Exemplify creative and innovative problem-solving of complex professional challenges through the application data analytics in the business domain

```{r}
library(dplyr)
library(skimr)
library(tidyverse)

#Get the data
df <- read.csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-11-03/ikea.csv')
```

There is a total of 3694 columns and 14 rows in the dataframe

```{r}
#Explore the data
#Display the first 10 rows
head(df)
#Display data type using the skim function
skim(df)
```
Using the skim fuction, we notice a significant amount of missing values in the depth, height and width variables. Number of missing values are 1464, 988 and 589 respectively, accounting for approximately 40%, 28% and 16% of the corresponding variables.
```{r}
#Count the number of categories
df %>% count(category, sort=TRUE)
```
Upon exploration, there are 17 categories within the IKEA sales data. 'Tables & desks' category has the highest number of items (612), and 'Room dividers' category has the lowest number of items (13).
```{r}
#Visualise number of categories
df %>% add_count(category) %>%
  mutate(category_fct = fct_reorder(category, n)) %>% 
  ggplot(aes(category_fct))+
  geom_bar() +
  geom_text(aes(label = n, y = n), nudge_y = 20)+
  labs(x="Number Of Items",
       y="Category",
       title="Number of Items Per Category")+
  coord_flip()
```


